Informing policy via dynamic models: Cholera in Haiti

### 2022-12-19 ms.Rnw
Refactored files, addressed some of Ed's comments

# Number of particles and simulations to use for pfilter and project from filter, respectively.
h1_scen_NP   <- switch(RUN_LEVEL, 50, 500, 5000)
h1_scen_sims <- switch(RUN_LEVEL, 20, 100,  500)

@@

      # project vacc scenario, with filtering dist, and model.
      h1_S2_sims <- project_from_filter(mod = s2, end_states = end_states, nsims = h1_scen_NP)

@@

      # project vacc scenario, with filtering dist, and model.
      h1_S4_sims <- project_from_filter(mod = s4, end_states = end_states, nsims = h1_scen_NP)

@@

      # project vacc scenario, with filtering dist, and model.
      h1_S3_sims <- project_from_filter(mod = s3, end_states = end_states, nsims = h1_scen_NP)

@@

      # project vacc scenario, with filtering dist, and model.
      h1_S1_sims <- project_from_filter(mod = s1, end_states = end_states, nsims = h1_scen_NP)

@@

<<Load Model 3 Vacc Scenarios, message=FALSE, include=FALSE>>=
NP_BPF <- switch(RUN_LEVEL, 50, 200, 1000)
NSIM   <- switch(RUN_LEVEL, 10,  50,  500)

>>>>

# Number of particles and simulations to use for pfilter and project from filter, respectively.
h1_scen_NP   <- switch(RUN_LEVEL, 50, 500, 5000)
h1_scen_sims <- switch(RUN_LEVEL, 20, 100, 1000)

@@

      # project vacc scenario, with filtering dist, and model.
      h1_S2_sims <- project_from_filter(mod = s2, end_states = end_states, nsims = h1_scen_sims)

@@

      # project vacc scenario, with filtering dist, and model.
      h1_S4_sims <- project_from_filter(mod = s4, end_states = end_states, nsims = h1_scen_sims)

@@

      # project vacc scenario, with filtering dist, and model.
      h1_S3_sims <- project_from_filter(mod = s3, end_states = end_states, nsims = h1_scen_sims)

@@

      # project vacc scenario, with filtering dist, and model.
      h1_S1_sims <- project_from_filter(mod = s1, end_states = end_states, nsims = h1_scen_sims)

@@

<<Load Model 3 Vacc Scenarios, message=FALSE, include=FALSE>>=
NP_BPF <- switch(RUN_LEVEL, 50, 200, 2000)
NSIM   <- switch(RUN_LEVEL, 10,  50, 1000)
